\section{Query Resolution Recorder (QRR)}
\label{sec:qrr}
% Chris
Answering a question using the deep web requires one to navigate
through a sequence of one or more web pages and links.  Many of the
accesses involve clicks through web forms to resulting pages.  We have
developed a model that represents the various actions a user may carry
out during this process.

During the answer retrieval process, a user discovers an element of
the query's result on a web page.  Next, she highlights that element,
typically a text string.  This highlight allows the QRR to record the
source of the query's answer.  The QRR stores all information from the
user query in our data store.  When the user submits a web form she
may associate each of the form's inputs with one of our stored context
classes.

The discovery process can be broken down into three cases:
\begin{enumerate}
\item The user typed in a URL and highlighted part of or all the
  answer.
\item The user typed in a URL, clicked a link, and found part or all
  of the answer.
\item The user typed in a URL, filled out a form, and found part or
  all of the answer on a subsequent page.
\end{enumerate}

Any discovery process consists of a sequence of these transactions.
Additionally, data collected for inputs and outputs may be found
during any stage of the complete discovery process.  An output
collected during one stage of an extraction may be the input to a
subsequent stage in the extraction.  The QRR builds the completed user
collection process into a QRM.  The following is a mathematical
formulation of information collected for user web interactions.

A QRM is a 5-tuple $Z = \left< \Upsilon, \Omega, P, M, R, A \right>$ such that:

\begin{enumerate}

\item $\Upsilon$ is the sequence of input categories $\left<
  \Upsilon_{1}, \Upsilon_{2}, \Upsilon_{3}, \Upsilon_{4} \right>$
  where $\Upsilon_{1}$ represents the \emph{who} context of the
  associated query, $\Upsilon_{2}$ represents the \emph{what} context,
  $\Upsilon_{3}$ represents the \emph{when} context, and
  $\Upsilon_{4}$ represents the \emph{where} context.

\item $\Omega$ is the sequence of output categories $\left<\Omega_{1},
  \Omega_{2}, \Omega_{3}, \Omega_{4}\right>$ where $\Omega_{1}$
  represents the \emph{who} context of the associated query,
  $\Omega_{2}$ represents the \emph{what} context, $\Omega_{3}$
  represents the \emph{when} context, and $\Omega_{4}$ represents the
  \emph{where} context.

\item $P$ is an ordered list of web pages $P = \left<P_1,P_2,...,
  P_n\right>$ where $P_h =
  \left<U_h,\left<I_{h_1},I_{h_2},...,I_{h_u}\right>,\left<O_{h_1},O_{h_2},...O_{h_v}\right>\right>$
  for $1 \leq h \leq n$, $u = \left| I_h \right|$, $v = \left| O_h
  \right|$. $P_h$ is a triple comprised of a URL $U_h$, a sequence of
  input arguments, and a sequence of output results.  \\ Let $I_{\$} =
  \bigcup_{j=1}^{4} I_{\downarrow_j}$ be the set of the selector
  expressions for the inputs of a query and $O_{\$} =
  \bigcup_{j=1}^{4} O_{\downarrow_j}$ be the set of selectors
  expressions for the outputs of a query.  \\ Let $K$ be the set of
  all string constants.
\begin{itemize}
\item URI $U_1 \in K$ is a string and \\ for $1 < g \leq n$, URI $U_g
  \in K \cup \left( \bigcup^{g-1}_{p=1} \left(
  \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$ where $1
  \leq h \leq \left| O_p \right| $,

\item for $1 < h < \left| I_1 \right|$, input $I_{1_h} \in K \cup
  I_{\$} \cup O_{\$}$ and \\ for $1 < g <= n$, then for $1 < h <
  \left| I_g \right|$, input $I_{g_h} \in K \cup I_{\$} \cup O_{\$}
  \cup \left( \bigcup^{g-1}_{p=1} \left(
  \bigcup^{\left|O_p\right|}_{h=1}O_{p_h} \right)\right)$.
\end{itemize}

\item $M$ is a map between $\Upsilon$, $K$, $\Omega$ to page list inputs $I_h$.

\item $R$ is an ontological realm. 

\item $A$ is the sequence of outputs from $\Upsilon$, $K$, and
  $\Omega$ representing the answer.

\end{enumerate}

%-------------------------------------------------------------------------------

%\subsection{Generalization}
% Christan
The response pages created by querying web forms are dynamically
generated with a templated structure. This generalization per page is
done using the GenPath algorithm developed by Badica et
al. \cite{Badica06}. Additionally, the community may be able to answer
a particular SSQ using many different page interactions. Therefore, we
use a method of generalizing extraction path to a result across
pages. This method removes unnecessary page interactions and finds the
shortest path to the result pages.

Websites wrapped by a system such as this are highly susceptible to
structural changes \cite{TanZMG07}. Generalizing the extraction paths
helps overcome small structural changes. If a website changes to the
point where a QRM is no longer useful, the QRM is not considered
fresh. User ratings of QRM freshness can be employed in the SSQ matching
process detailed in Section \ref{sec:ssq}.

%-------------------------------------------------------------------------------
