\section{Query Re-execution}
% Chris
When a user submits a new query to the Morpheus system, one or more
stored QRMs are executed to obtain results. A QRM contains an XML
script representing an algorithm that will obtain the required result.
The evaluation of this script by the QRE simulates the behavior of a
human browsing the web, that is, clicking buttons to follow links,
submitting forms, highlighting data, cutting and pasting text, and
constructing an answer in the form of a text string.

There is greater complexity in dealing with web forms than with links.
At present, the GET form submission method is used. This means that in preparation to 
submit a form, the Morpheus System builds a querystring consisting of name-value pairs.
For a given form, there may be text fields, drop-down boxes, and among other components.
In order to support form submission in such circumstances, the QRE performs
different actions based upon the input type. For text fields, simply
adding a key/value pair to the query string suffices. For a drop-down
box, the QRE extracts the form element to find the appropriate value to
include in the query string. It does this by examine each option in the drop-down and 
matching the user's input to the text field in the option. The value attribute of the option
is then added to the querystring. The value and text attributes of a drop-down option might 
be the same, but they are not guaranteed to be. 

All input data are kept in an internal table. The QRM script contains
keys that allow the QRE to map SSQ inputs from the table to the
appropriate form inputs. Furthermore, highlighted text segments
collected during execution of the script are stored in the table.
Once all actions in the script have been carried out, the QRE returns
the textual answer this process has created. This answer is then be
rendered in a browser displayed to the user.
