\subsection{Query Re-execution}
% Chris
When a user submits a new query to the Morpheus system, one or more
stored Query Resolution Methods are executed to obtain results. A QRM
consists of an XML script which instructs the Query Resolution
Executor how to obtain the required result. The Query Resolution
Executor may "click" links, submit forms or highlight and save
important pieces of html, including answers. At the present, the GET
form submission method is used.  There is greater complexity in
dealing with web forms than with links. For a given form, there may be
text fields, drop-down boxes, radio buttons etc. In order to support
form submission in such circumstances the QRE will take different
actions based on the input type. For text fields, simply adding a
key/value pair to the querystring suffices. For a drop-down box, the
QRE extracts the form element and performs a lookup on its options to
find the appropriate value to include in the querystring.  All input
data as well as highlighted HTML is kept in an internal hash
table. The QRM script contains keys which allow the QRE to map SSQ
inputs from the table to the appropriate form inputs. Furthermore,
highlights which are collected during execution are stored in the hash
table.  Once all pages included in the script have been visited, the
QRE returns the HTML snippet containing the answer. This answer can
then be rendered in a browser. Normally a list of QRMs, sorted by
relevance, are given to the QRE. Therefore after execution a list of
results is returned in order of relevance.
