\section{Results}
\label{sec:results}

% 3-4 queries 
% Human made ontology 
% Topic Models 

First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets. For each of the classes in the ontology we built corpora from the corresponding pWikipedia pages. Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.

In Table \ref{tbl:nlp_engine_parse} we show the data output by the Morpheus parse of the query.  It extracts the \emph{wh}-term that classifies the sentence as a question, identifies the answer class, and locates descriptive phrases to produce the answer. Finally, the engine produces n-grams from phrases in the descriptive information sections.

Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance. Table \ref{tbl:term_classes} shows the eight best term classes and their probabilities for automotive queries.

\begin{table}[!]\footnotesize
	\begin{tabular}{|l|p{4.9cm}|}
		\hline 
		\emph{wh}-term & what \\
		\hline 
		descriptive phrases & \small 1997 Toyota Camry V6 \\
		\hline 
		asking for & size tires \\
		\hline 
		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
		\hline
	\end{tabular}
	\caption{The output of NLP engine}
	\label{tbl:nlp_engine_parse} 
\end{table}

\begin{table}[!]\footnotesize

\begin{tabular}{| p{3.5cm} | p{1.45cm} | r |}
\hline 
Term & Class & $P(Class|Term)$ \\ \hline
1997 & Sedans & 404132.77e-14\\ 
1997 Toyota & Engines & 7.90e-14\\ 
Toyota  & Sedans & 3486670.15e-14\\ 
Toyota Camry & Sedans & 12147.23e-14\\ 
Toyota Camry V6 & Coupes & 13.80e-14\\ 
Camry & Sedans & 312034.20e-14\\ 
Camry V6 & Coupes & 13.80e-14\\ 
V6 & Sedans & 4464535.40e-14\\ \hline
\end{tabular}        

\caption{Term classes and probabilities}
\label{tbl:term_classes}   

\end{table}

We found the best classes for the terms in the candidate SSQ. We calculated the class divergence between these classes and the qualified SSQ classes in the QRM store. QRMs are ranked based upon the relevance score and the class divergence measure. Table \ref{tbl:ranked_queries} shows the thAnswers are produced by the QRE, a python back end.ree highest ranked queries. Finally, we execute the best QRMs and display the results to the user.



\begin{table}[!]\footnotesize

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
	\hline
	Query & Tagged Classes & Score\\ 
	\hline
	\small A 1997 Toyota Camry V6 needs what size tires? & \small Sedan, Automobile, Engine, Manufacturer & 0.91\\ 
	\hline 
	\small What is the tire size for a 1998 Sienna XLE Van? & \small Van, Manufacturer & 0.72\\
	\hline 
	\small Where can I buy an engine for a Toyota Camry V6? & \small Sedan, Automobile Engine, Manufacturers & 0.74 \\
	\hline 
%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
\end{tabular}

\caption{Highest ranked queries}
\label{tbl:ranked_queries}   

\end{table}


%\subsection{Discussion}
\section{Conclusion}

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs. The classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.  These terms are the input to existing answer paths and we re-execute these paths with the new input to produce answers.

Our solution is composed a web front end where users can ask questions. The QRR was developed as a Firefox plugin and an associated C\# application.  Our similarity measures were coded using Java and open source libraries. Answers are produced by the QRE, a python back end. The data is stored in a PostresSQL database.


%Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
Topic modeling provides a promising approach to identifying pages relevant to a class in a more automated manner. We believe our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may remove the user from the answer path generation process.

Additionally, we are investigating methods of merging QRMs to answer compound questions.  This will allow us to chain QRMs using the principles of transform composition \cite{transformscout}.


% 2. Current stage of the project 
% 3. Expected contribution to the topics of interest supported by iiWAS2010 
